Reduced plasticity and relative variance in physiological rates of ectotherm populations under climate change

### 2024-06-20 ms.qmd
Fixed up Fig 3 (previous fig 2). There were some mistakes in the objects and life-history means were being named the same, overwriting means for acute and acclim. This is fixed now.

# Now, lets calculate the contrasts between acute a and j as well as acclim a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
    # Marine 
         m_acute <-  pred[1,] - pred[3,] # Contrasts acute a and acute j values for marine species
        m_acclim <-  pred[4,] - pred[2,] # Contrasts acclim a and acute j values for marine species
    # Freshwater
            f_ad <- 4
         f_acute <- pred[1+f_ad,] - pred[3+f_ad,] # Contrasts acute a and acute j values for freshwater species
        f_acclim <-  pred[4+f_ad,] - pred[2+f_ad,] # Contrasts acclim a and acute j values for freshwater species
    # Terrestrial
            t_ad <- 8
         t_acute <- pred[1+t_ad,] - pred[3+t_ad,] # Contrasts acute a and acute j values for terrestrial species
        t_acclim <-  pred[4+t_ad,] - pred[2+t_ad,]  # Contrasts acclim a and acute j values for terrestrial species

  # Acute differences between a and j across all habitats
     acute_all <- c(m_acute, f_acute, t_acute); mean(acute_all); quantile(acute_all, c(0.025, 0.975)); pmcmc(acute_all)
    acclim_all <- c(m_acclim, f_acclim, t_acclim)

@@

  ggsave(filename = "fig2_unedited_18June.pdf", path = "./output/figures/", phylo, device = "pdf", width = 10, height = 9, units = "in")

@@

```{r, lncvrq10}
#| label: lncvrq10
#| echo: false
#| warning: false
#| error: false
#| include: false
#| cache: true

@@

```{r, fig-3}
#| label: fig-3
#| fig-cap:  **A)** Mean acute and acclimation $lnRR_{Q_{10}}$ across marine, freshwater, and terrestrial systems. **C)** Mean acute and acclimation $lnCVR_{Q_{10}}$ across traits for marine, freshwater and terrestrial systems. Note there were no differences between acute and acclimation $Q_{10}$ types. For both plots, k = total number of effect size estimates while the numbers in brackets indicate the number of species. Sample sizes are the same for panel A and B. Thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI). $\Beta$ values are the contrasts between acute and acclimation means. $\mu$ values are the overall mean $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ averaged across acute and acclimdation types within each habitat type. In both cases, their 95% CI's are indicated within square brackets. $p_{MCMC}$ values are the posterior probability of the contrast being different from zero."
#| warning: false
#| echo: false

@@

  p3a <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left", trunk.size = 1.8, branch.size = 2.8, alpha = 0.4) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
  theme(legend.direction = "vertical") +

  annotate("text", x = 1.5, y = 0, 
         label =TeX(paste0("$\\beta = $", round(model1.2$b[4], 2), "[", round(model1.2$ci.lb[4], 2)," to ", round(model1.2$ci.ub[4], 2), "] ", " $p_{MCMC}$ < 0.001")), hjust = 0, size = 8) + 
  annotate("text", x = 1.20, y = -0.5, 
         label =paste0(round(mean(change_f), 3), "%"), hjust = 0, size = 8) + labs(shape = "Type") +

  annotate("text", x = 2.5, y = 0, 
         label =TeX(paste0("$\\beta = $", round(mean(m_acclim - m_acute), 2), "[", round(quantile(m_acclim - m_acute, 0.025), 2)," to ", round(quantile(m_acclim - m_acute, 0.975),2), "] ", " $p_{MCMC}$ = 0.01")), hjust = 0, size = 8) + 
  annotate("text", x = 2.20, y = -0.5, 
         label =paste0(round(mean(change_m), 3), "%"), hjust = 0, size = 8) +

  annotate("text", x = 3.5, y = 0, 
         label =TeX(paste0("$\\beta = $", round(mean(t_acclim - t_acute), 2), "[", round(quantile(t_acclim - t_acute, 0.025), 2)," to ", round(quantile(t_acclim - t_acute, 0.975),2), "] ", " $p_{MCMC}$ = 0.36")), hjust = 0, size = 8) + 
  annotate("text", x = 3.20, y = -0.5, 
         label =paste0(round(mean(change_t), 3), "%"), hjust = 0, size = 8) +

@@

  annotate("text", x = x1, y = -1.3, 
           label =TeX(paste0("$\\mu = $", round(mean(f_cvr_mean), 3), "[", round(quantile(f_cvr_mean, 0.025), 2)," to ", round(quantile(f_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
  annotate("text", x = x1-0.15, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(f_cvr_mean), digit = 2))), hjust = 0, size = 6) + 
  annotate("text", x = x1-0.15, y = 1, 
           label =paste0(round(mean(exp(f_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) +

  annotate("text", x = x2, y = -1.3, 
           label =TeX(paste0("$\\mu = $", round(mean(m_cvr_mean), 3), "[", round(quantile(m_cvr_mean, 0.025), 2)," to ", round(quantile(m_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
  annotate("text", x = x2-0.15, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(m_cvr_mean), digit = 2))), hjust = 0, size = 6) +
  annotate("text", x = x2-0.15, y = 1, 
           label =paste0(round(mean(exp(m_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) +

  annotate("text", x = x3, y = -1, 
           label =TeX(paste0("$\\mu = $", round(mean(t_cvr_mean), 3), "[", round(quantile(t_cvr_mean, 0.025), 2)," to ", round(quantile(t_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
  annotate("text", x = x3-0.15, y = 1, 
           label =paste0(round(mean(exp(t_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
    annotate("text", x = x3-0.15, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(t_cvr_mean), digit = 3))), hjust = 0, size = 6) + ylim(-1.5, 1.75) + 
    annotate("text", label= paste0("k = ", k_cvr$k, " (", k_cvr$sdy, ")"), x = c(0.8, 1.8, 2.8), y = 1.3, size = 5) + ylim (-1.5, 1.5)

  p3b <- p3b + theme_classic() + theme(axis.title  = element_text(size = 24),
                                       axis.text = element_text(size = 24),
                                       axis.text.y = element_blank(),
                                       legend.title = element_text(size = 30),
                               legend.text = element_text(size = 24),
                               title = element_text(size = 24), legend.position = "top")

  fig3 <- (p3a + p3b) + plot_annotation(tag_levels = "A", tag_suffix = ")")

   ggsave(fig3, filename = "./output/figures/fig3_r1.pdf", width = 9.3, height = 8.8)

@@

```{r, fig-accl_time}
#| label: fig-accl_time
#| fig-cap: "Bubble plot of the relationship between $lnRR_{Q_{10}}$ and acclimation time for terrestrial (green), marine (orange) and freshwater (blue) habitats. Acclimation time is centered around the mean acclimation time (37.5 days) in the data. Not all studies reported acclimation time hence the total number of effects, k, was 1767."
  col <- c("#0871B9", "#F3B40D", "#1BB908")

>>>>

# Now, lets calculate the contrasts between acute a and j as well as acclim a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
    # Marine 
         m_acute_lh <-  pred[1,] - pred[3,] # Contrasts acute a and acute j values for marine species
        m_acclim_lh <-  pred[4,] - pred[2,] # Contrasts acclim a and acute j values for marine species
    # Freshwater
            f_ad <- 4
         f_acute_lh <- pred[1+f_ad,] - pred[3+f_ad,] # Contrasts acute a and acute j values for freshwater species
        f_acclim_lh <-  pred[4+f_ad,] - pred[2+f_ad,] # Contrasts acclim a and acute j values for freshwater species
    # Terrestrial
            t_ad <- 8
         t_acute_lh <- pred[1+t_ad,] - pred[3+t_ad,] # Contrasts acute a and acute j values for terrestrial species
        t_acclim_lh <-  pred[4+t_ad,] - pred[2+t_ad,]  # Contrasts acclim a and acute j values for terrestrial species

  # Acute differences between a and j across all habitats
     acute_all_lh <- c(m_acute_lh, f_acute_lh, t_acute_lh); mean(acute_all); quantile(acute_all, c(0.025, 0.975)); pmcmc(acute_all)
    acclim_all_lh <- c(m_acclim_lh, f_acclim_lh, t_acclim_lh)

@@

  #ggsave(filename = "fig2_unedited_18June.pdf", path = "./output/figures/", phylo, device = "pdf", width = 10, height = 9, units = "in")

@@

```{r, lncvrq10}
#| label: lncvrq10
#| echo: false
#| warning: false
#| error: false
#| include: false
#| cache: false

@@

```{r, fig-2}
#| label: fig-2
#| fig-cap:  **A)** Mean acute and acclimation $lnRR_{Q_{10}}$ across ectotherms in marine, freshwater, and terrestrial habitats. **B)** Mean acute and acclimation $lnCVR_{Q_{10}}$ across ectotherms in marine, freshwater and terrestrial habitats. For both plots, k = total number of effect size estimates while the numbers in brackets indicate the number of species. Sample sizes are the same for panel A and B. Thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI). $\Beta$ values are the contrasts between acute and acclimation means within each habitat. $\mu$ values are the overall meta-analytic means averaged across acute and acclimation types within each habitat type. In both cases, their 95% CI's are indicated within square brackets. $p_{MCMC}$ values are the posterior probability of the contrast or overall meta-analytic mean being different from zero. For ease of visualisation, all raw data for both acute and acclimation type effect sizes are presented as circles."
#| warning: false
#| echo: false

@@

  p3a <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 20, legend.pos = "top.left", trunk.size = 1.8, branch.size = 2.8, alpha = 0.4) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
  theme(legend.direction = "vertical") +

  annotate("text", x = 1.5, y = -0.30, label =TeX(paste0("$\\beta = $", round(mean(f_acclim - f_acute), 2), "[", round(quantile(f_acclim - f_acute, 0.025), 2)," to ", round(quantile(f_acclim - f_acute, 0.975), 2), "] ", " $\\,p_{MCMC}$ < 0.001")), hjust = 0, size = 8) + 
  annotate("text", x = 1.20, y = -0.5, label =paste0(round(mean(change_f), 3), "%"), hjust = 0, size = 8) + labs(shape = "Type") +

  annotate("text", x = 2.5, y = -0.30, label =TeX(paste0("$\\beta = $", round(mean(m_acclim - m_acute), 2), "[", round(quantile(m_acclim - m_acute, 0.025), 2)," to ", round(quantile(m_acclim - m_acute, 0.975),2), "] ", " $\\,p_{MCMC}$ = 0.01")), hjust = 0, size = 8) + 
  annotate("text", x = 2.20, y = -0.5, label =paste0(round(mean(change_m), 3), "%"), hjust = 0, size = 8) +

  annotate("text", x = 3.5, y = -0.30, label =TeX(paste0("$\\beta = $", round(mean(t_acclim - t_acute), 2), "[", round(quantile(t_acclim - t_acute, 0.025), 2)," to ", round(quantile(t_acclim - t_acute, 0.975),2), "] ", "$\\,p_{MCMC}$ = 0.36")), hjust = 0, size = 8) + 
  annotate("text", x = 3.20, y = -0.5, label =paste0(round(mean(change_t), 3), "%"), hjust = 0, size = 8) +

@@

  annotate("text", x = x1, y = -1.5, label =TeX(paste0("$\\mu = $", round(mean(f_cvr_mean), 3), "[", round(quantile(f_cvr_mean, 0.025), 2)," to ", round(quantile(f_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 8) + 
         annotate("text", x = x1, y = 0.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
  annotate("text", x = x1-0.20, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(f_cvr_mean), digit = 2))), hjust = 0, size = 8) + 
  annotate("text", x = x1-0.20, y = 1, label =paste0(round(mean(exp(f_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 8) +

  annotate("text", x = x2, y = -1.5, label =TeX(paste0("$\\mu = $", round(mean(m_cvr_mean), 3), "[", round(quantile(m_cvr_mean, 0.025), 2)," to ", round(quantile(m_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 8) + 
     annotate("text", x = x2, y = 0.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
  annotate("text", x = x2-0.20, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(m_cvr_mean), digit = 2))), hjust = 0, size = 8) +
  annotate("text", x = x2-0.20, y = 1, label =paste0(round(mean(exp(m_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 8) +

  annotate("text", x = x3+0.10, y = -1.5, label =TeX(paste0("$\\mu = $", round(mean(t_cvr_mean), 3), "[", round(quantile(t_cvr_mean, 0.025), 2)," to ", round(quantile(t_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 8) + 
  annotate("text", x = x3+0.10, y = 0.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
  annotate("text", x = x3-0.10, y = 1, label =paste0(round(mean(exp(t_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 8) + 
  annotate("text", x = x3-0.10, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(t_cvr_mean), digit = 3))), hjust = 0, size = 8) +

    labs(shape = "Type") +
    annotate("text", label= paste0("k = ", k_cvr$k, " (", k_cvr$sdy, ")"), x = c(0.8, 1.8, 2.8), y = 1.3, size = 5) + ylim (-1.5, 1.5)

  p3b <- p3b + theme_classic() + theme(axis.title  = element_text(size = 24),
                                       axis.text = element_text(size = 24),
                                       axis.text.y = element_blank(),
                                       legend.title = element_text(size = 30),
                               legend.text = element_text(size = 24),
                               title = element_text(size = 24), legend.position = "top") + guides(shape = "none")

  fig3 <- (p3a + p3b) + plot_annotation(tag_levels = "A", tag_suffix = ")")
  fig3
  ggsave(fig3, filename = "./output/figures/fig3_r1.pdf", width = 21.88, height = 9)

@@

#### How acclimation time is related to $lnRR_{Q_{10}}$ 
```{r, fig-accl_time}
#| label: fig-accl_time
#| fig-cap: "Bubble plot of the relationship between $lnRR_{Q_{10}}$ and acclimation time for terrestrial (green), marine (orange) and freshwater (blue) habitats. Acclimation time is centered around the mean acclimation time (37.5 days) in the data. Not all studies reported acclimation time hence the total number of effects, k, was 1767."
  col <- c("#0871B9", "#F3B40D", "#1BB908")
